MNSA PILOT DATA

### 2021-06-20 Interview Duration.Rmd
Last day of pilot
Data from the pilot survey

df <-  read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-16-14-45-28.xlsx")

@@

df <- df %>% 
  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
                                  TRUE ~ "no"))
df$not_eligible
# import loop data
indiv_df <- read_excel("input/raw_data/Final__V10__REACH_oPt_Kobo_MSNA_May_2021_V8_27052021_-_all_versions_-_False_-_2021-06-07-08-58-28.xlsx", sheet = "member")

@@

#  data collected today
today_df <- replaced_df %>% 
  filter(today == assessment_start_date)
```
**Duration of surveys**
```{r}
survey_duration <- today_df %>% 
  filter(today_df$consent == "yes") %>% 
  group_by(Enumerator = enumerator_num) %>% 
  summarise(
    Median_duration = round(median(interview_duration, na.rm = T),0)
  )
survey_duration
```
```{r}
survey_duration_2 <- today_df %>% 
  filter(today_df$consent == "yes") %>% 
  dplyr::select(enumerator_num,interview_duration)
survey_duration_2
```

@@

*Surveys with less Than  30 mins*
```{r}
duration_less_30 <- today_df %>% 
  filter(today_df$consent == "yes" & interview_duration <= 30) %>% 
  dplyr::select(enumerator_num,interview_duration)
duration_less_30
```

>>>>

df <-  read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx")

@@

df <- df %>% 
  mutate(not_eligible = case_when(is.na(hh_size) ~ "yes",
                                  TRUE ~ "no"))
df$not_eligible
# import loop data
indiv_df <- read_excel("input/raw_data/FINAL_Pilot_V12_REACH_oPt_Kobo_MSNA_June_2021_13062021_2021-06-20-05-33-16.xlsx", sheet = "member")

@@

#  data collected today
today_df <- replaced_df %>% 
  filter(today == assessment_start_date)
```
**Duration of surveys**
```{r}
survey_duration <- today_df %>% 
  filter(today_df$consent == "yes") %>% 
  group_by(Enumerator = enumerator_num) %>% 
  summarise(
    Median_duration = round(median(interview_duration, na.rm = T),0)
  ) %>% 
arrange(desc(Median_duration) )
survey_duration
```
```{r}
survey_duration_2 <- today_df %>% 
  filter(today_df$consent == "yes") %>% 
  dplyr::select(enumerator_num,interview_duration)
survey_duration_2
```

@@

*Surveys with less Than  40 mins*
```{r}
duration_less_30 <- today_df %>% 
  filter(today_df$consent == "yes" & interview_duration <= 40) %>% 
  dplyr::select(enumerator_num,interview_duration)
duration_less_30
```
